Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-04-09 docs/00-manuscripts/ieee/ieee-manuscript.tex
remove PCA correlation analysis figure and only use text

\subsection{Correlation among predictors}

A \ac{PCA} was done to analyse the correlation within the variables of the different feature sets (\autoref{fig:pca-pov}).

@@

The PCA-based correlation analysis in \autoref{fig:pca-pov} shows that, depending on the feature set, between two (HR) and five (VI) \ac{PC} are needed to explain 90\% of variance.
The less PCs are needed to reach a high proportion of variance explained the more similar the individual features are to each other.
Hence, a high intra-feature correlation can be observed for feature set HR which reaches 98\% with only two PCs.
Feature sets NRI and VI are more diverse and require four (NRI) and five (VI) PCs to explain 90\% of the variance in the data, respectively.

% \begin{figure} [t!]
% 	\centering
% 	\begin{center}
% 		\includegraphics[width=0.48\textwidth] {pca-pov-comparison-1.pdf}
% 		\caption{Proportion of variance explained by a Principal Component Analysis for all feature sets.
% 		To show at least 2 PC for every feature set, the target POV was set to 98\% for VI and NRI and to 90\% for HR.}
% 		\label{fig:pca-pov}
% 	\end{center}
% \end{figure}

>>>>

@@

The PCA-based correlation analysis showed that, depending on the feature set, between two (HR) and 42 (NRI) \ac{PC} are needed to explain 95\% of variance.
The less PCs are needed to reach a high proportion of variance explained the more similar the individual features are to each other.
Hence, a high intra-feature correlation can be observed for feature set HR which reaches 96\% with only two PCs.
Feature sets NRI and VI are more diverse and require 42 (NRI) and 12 (VI) PCs to explain 95\% of the variance in the data, respectively.
